Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-02 results.tex
Corrected figure reference
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@842 ccdd05d5-56c1-461a-bf98-85f6876523b4

We expect two known contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ basis, which is fundamental, and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  We have measured the
effect of the resampling in the pipeline alone on a single waveform to gauge
the magnitude of the loss.  It is shown in figure \ref{fig:resamp_mm} as a
function of the quality of the {\tt audioresample} element (which is
proportional to the filter length used).  In both cases we have to compare the
\SNR\ loss to the expected \SNR\ loss that arises from the discreteness of the
template bank which is typically $\sim 3\%$.  We will consider a comparable
\SNR\ loss to be tolerable, but ideally would like to have a factor of 10 lower
loss from the \lloid\ implementation (i.e. no more than $\sim 0.3 \%$).

>>>>

We expect two known contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ basis, which is fundamental, and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  We have measured the
effect of the resampling in the pipeline alone on a single waveform to gauge
the magnitude of the loss.  It is shown in figure \ref{fig:hist-interpolate} as a
function of the quality of the {\tt audioresample} element (which is
proportional to the filter length used).  In both cases we have to compare the
\SNR\ loss to the expected \SNR\ loss that arises from the discreteness of the
template bank which is typically $\sim 3\%$.  We will consider a comparable
\SNR\ loss to be tolerable, but ideally would like to have a factor of 10 lower
loss from the \lloid\ implementation (i.e. no more than $\sim 0.3 \%$).
